Causal Roadmap

### 2023-01-12 docs/causal_roadmap.qmd
Converted to qmd

```{r setup, include=FALSE}
library(tidyverse)
```

```{r, echo=FALSE}
# Type of adjustment set from DAG
type.mas <- "minimal"
# Type of effect to be estimated from DAG
type.effect <- "direct"
```

@@

```{r causal-graph, echo=FALSE, fig.cap="Causal graph corresponding to structural equations.", fig.height=3, fig.width=3}
causal.graph <- ggdag::dagify(A ~ W + U_A, Y ~ W + A + U_Y, W ~ U_W, 
                              exposure = "A", outcome = "Y") %>%
  ggdag::tidy_dagitty()
ggdag::ggdag(causal.graph) + ggdag::theme_dag()
```

@@

```{r echo=FALSE, fig.cap="Simplified DAG for research question 1."}
sdag1 <- ggdag::dagify(X_ti ~ W_t, 
                       Y ~ W_t + X_ti, 
                       exposure = "X_ti", outcome = "Y") %>%
  ggdag::tidy_dagitty() %>%
  ggdag::ggdag(text_size = 2, node_size = 10) + ggdag::theme_dag() +
  ggplot2::ggtitle("RQ1")
```

```{r, echo=FALSE}
ggpubr::ggarrange(sdag1, ..., 
                  ncol = x, nrow = y)
```

@@

```{r, echo=FALSE}
source("../DAGs/dag_v1.R")
source("../code/dags.R")

@@

```{r, echo=FALSE, fig.cap="DAG for Research question 1.", fig.height=10, fig.width=18}
dag.rq1 <- dags$rq1 %>%
  dagitty::dagitty()
dag.rq1 %>% ggdag::tidy_dagitty() %>%
  ggdag::ggdag_status(text_size = 10, text_col = "black") +
  ggdag::theme_dag() + ggdag::scale_adjusted() +
  ggplot2::theme(legend.text = ggplot2::element_text(size = 20))
```

@@

```{r, echo=FALSE}
dagitty::adjustmentSets(x = dag.rq1, 
                        type = type.mas, effect = type.effect)
```

>>>>

```{r}
#| label: setup
#| include: false
library(tidyverse)
```

```{r}
#| echo: false
# Type of adjustment set from DAG
type.mas <- "minimal"
# Type of effect to be estimated from DAG
type.effect <- "direct"
```

@@

```{r}
#| label: causal-graph
#| echo: false
#| fig.cap: Causal graph corresponding to structural equations.
#| fig.height: 3.0
#| fig.width: 3.0
causal.graph <- ggdag::dagify(A ~ W + U_A, Y ~ W + A + U_Y, W ~ U_W, 
                              exposure = "A", outcome = "Y") %>%
  ggdag::tidy_dagitty()
ggdag::ggdag(causal.graph) + ggdag::theme_dag()
```

@@

```{r}
#| echo: false
#| fig.cap: Simplified DAG for research question 1.
sdag1 <- ggdag::dagify(X_ti ~ W_t, 
                       Y ~ W_t + X_ti, 
                       exposure = "X_ti", outcome = "Y") %>%
  ggdag::tidy_dagitty() %>%
  ggdag::ggdag(text_size = 2, node_size = 10) + ggdag::theme_dag() +
  ggplot2::ggtitle("RQ1")
```

```{r}
#| echo: false
ggpubr::ggarrange(sdag1, ..., 
                  ncol = x, nrow = y)
```

@@

```{r}
#| echo: false
source("../DAGs/dag_v1.R")
source("../code/dags.R")

@@

```{r}
#| echo: false
#| fig.cap: DAG for Research question 1.
#| fig.height: 10.0
#| fig.width: 18.0
dag.rq1 <- dags$rq1 %>%
  dagitty::dagitty()
dag.rq1 %>% ggdag::tidy_dagitty() %>%
  ggdag::ggdag_status(text_size = 10, text_col = "black") +
  ggdag::theme_dag() + ggdag::scale_adjusted() +
  ggplot2::theme(legend.text = ggplot2::element_text(size = 20))
```

@@

```{r}
#| echo: false
dagitty::adjustmentSets(x = dag.rq1, 
                        type = type.mas, effect = type.effect)
```
